Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-10-07 GWLDCII.tex
added my thanks, same as the other paper

\title{Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators}
\author{Susama Agarwala, Si\^an Fryer, and Karen Yeats}
%\date{}

>>>>

\title{Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators}
\author{Susama Agarwala, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and though some the time this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
%\date{}
